---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# dplaceR

<!-- badges: start -->
<!-- badges: end -->

dplaceR provides an R interface to [D-PLACE](https://d-place.org) (Database
of Places, Language, Culture and Environment), a cross-cultural database
linking ethnographic, linguistic, environmental, and geographic information
for societies around the world.

A snapshot of the D-PLACE [CLDF](https://cldf.clld.org/) dataset is bundled
with the package, so no internet connection is needed after installation,
and results are reproducible across dplaceR versions. See `dp_citation()`
for exactly which release is bundled.

## Installation

You can install the development version of dplaceR from
[GitHub](https://github.com/) with:

```r
# install.packages("remotes")
remotes::install_github("jasonahodgson/dplaceR")
```

## Example

Browse societies and variables, look up the coded values for a variable,
and join them to society information in one step:

```{r example}
library(dplaceR)

# Societies in a region
dp_societies(region = "Southern Africa")

# Find variables about a topic
dp_search_variables("descent")

# Codes for a categorical variable
dp_codes("B035")

# Analysis-ready table: values + society info + code labels
dp_variable_data("B035")
```

Language phylogenies are available too:

```{r trees}
dp_trees()

dp_tree("abkh1242")
```

## Citing dplaceR and D-PLACE

If you use dplaceR in published work, please cite the dplaceR package
itself, in addition to D-PLACE and the specific source dataset(s) your
variables come from:

```{r package-citation}
citation("dplaceR")
```

```{r citation}
dp_citation()
```

```{r contributions}
dp_contributions(contribution_id = "dplace-dataset-binford")
```
